An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-05-01 VLDB2026/main.tex
Update main.tex
change 4.2.2

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. The performance of CAPS is as good as that of Puck. The difference between them is that CAPS further groups the results by attributes within clusters. In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

@@

	\subsubsection{Robustness}In the following, we evaluate the robustness of \textcolor{blue}{attribute filtering algorithms.}

	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate the performance of these algorithms across different attribute distributions, we generate attribute} sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1. We evaluate all algorithms under these distributions on each dataset. The performance differences observed for the same algorithm across different datasets are relatively minor. Thus, due to space constraints, we present only the results on SIFT1M.

>>>>

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. \textcolor{red}{CAPS performs as well as Puck, but differs by further grouping results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

@@

	\subsubsection{Robustness}In the following, we evaluate the robustness of these algorithms.

	\textit{\textbf{Attribute Distribution.}} \textcolor{blue}{To evaluate} performance across different attribute distributions, we generate base and query attribute sets with 4 representative distributions—long-tailed, normal, power-law, and uniform—across the 6 datasets described in Section~4.1.1. We evaluate all algorithms under these distributions on each dataset. The performance differences observed for the same algorithm across different datasets are relatively minor. Thus, due to space constraints, we present only the results on SIFT1M.
